---
output:
  pdf_document: default
  html_document: default
---



# R repeat loop

* A repeat loop is used to iterate a block of code. It is a special type of loop in which there is no condition to exit from the loop. For exiting, we include a break statement with a user-defined condition. This property of the loop makes it different from the other loops.

* A repeat loop constructs with the help of the repeat keyword in R. It is very easy to construct an infinite loop in R.

* The basic syntax of the repeat loop is as follows:

```repeat {   
   commands   
   if(condition) {  
      break  
   }  
}```


```{r}
x<-c("i","love","you","babu")
```


```{r}
y<-4
```


```{r}
repeat
{
  print(x)
  y<-y+1
  if(y>10)
  {
    break
  }
  
}
```


```{r}
x = 1

# Repeat loop
repeat {

    print(x)
    
    # Break statement to terminate if x > 4
    if (x > 4) {
        break
    } 
    
    # Increment x by 1
    x = x + 1
    
}
```


```{r}
x = 1
sum = 0

# Repeat loop
repeat {

    # Calculate sum
    sum = sum + x
    
    # Print sum
    print(sum)
    
    # Increment x by 1
    x = x + 1
    
}
```


```{r}
```

